|

### 2023-01-31 paper.Rmd
autogit

Unfortunately, as shown in figure \@ref(fig:airfoil-runtime-total), for the experiment conducted on the airfoil dataset with 2 hidden layers a negative impact of pre-training can be observed for the DAE-GP runtime.

@@

>>>>

<!-- TODO: Disclaimer, Runtime is implementation dependant, no GPU use, etc... -->

```{r runtime_vars, echo=FALSE}

# Values are copied from file /eda-gp-2020/experiments/airfoil_2hl_150hn_fullRun_30gens/airfoil_2hl_150hn_fullRun_30gens_TimeBenchmark.ipynb

REG_TIME <- 5076.448
PT_TIME <- 14706.465
PT_TIME_NOSAMPLE <- 12536.889
```

Suprinsingly, as shown in figure \@ref(fig:airfoil-runtime-total), for the experiment conducted on the airfoil dataset with 2 hidden layers a strong negative impact of pre-training can be observed for the median runtime of DAE-GP. If the time spend on pre-training is included into the total runtime, the median duration for pre-trained DAE-GP over all 10 runs increases by a factor of `r round(PT_TIME / REG_TIME, 3)` from a median runtime of `r format(REG_TIME, scientific=F)` seconds for regular DAE-GP to `r format(PT_TIME, scientific=F)` seconds for the pre-trained algorithm. Even in the case where the time spend for pre-training is excluded from the total runtime, pre-training still increases the runtime of DAE-GP by a factor of `r round(PT_TIME_NOSAMPLE / REG_TIME, 3)` to `r format(PT_TIME_NOSAMPLE, scientific=F)` seconds.

@@

To investigate the strong negative impact of pre-training on DAE-GP runtime, I first studied the influence of pre-training on the median number of training epochs that had to be spend at each generation for the training of the DAE-LSTM models $M_g$. Figure \@ref(fig:airfoil-trainingEpochs) shows that pre-training, as expected, strongly reduces the number of training epochs that had to be executed at each generation until the termination condition was reached. By reducing the number of training epochs, pre-training should therefore reduce the runtime of DAE-GP.

### 2023-01-31 paper.tex
autogit

Johannes Gutenberg University Mainz}
\author{}
\date{\vspace{-2.5em}Date of Submission: 2023-01-30}

@@

>>>>

Johannes Gutenberg University Mainz}
\author{}
\date{\vspace{-2.5em}Date of Submission: 2023-01-31}

@@

One important argument for using pre-training with DAE-GP is that it might be a potential way to reduce the overall run-time of the algorithm by reducing the training time of each generation's DAE-LSTM model. Especially in the context of optimization problems where solutions have to be found numerous times in a time efficient manner (e.g.~Vehicle Routing in the Domain of Logistic Services), one major advantage of pre-training is that a pre-trained model can be re-used to optimize many instances of an optimization problem.

Unfortunately, as shown in figure \ref{fig:airfoil-runtime-total}, for the experiment conducted on the airfoil dataset with 2 hidden layers a strong negative impact of pre-training can be observed for the median runtime of DAE-GP. If the time spend on pre-training is included into the total runtime, the median duration for pre-trained DAE-GP over all 10 runs increases by a factor of 2.897 from a median runtime of 5076.448 seconds for regular DAE-GP to 14706.47 seconds for the pre-trained algorithm. Even in the case where the time spend for pre-training is excluded from the total runtime, pre-training still increases the runtime of DAE-GP by a factor of 2.47 to 12536.89 seconds.
